Adaptive Distance Metric Selection for Supervised Classification

### 2016-10-21 latex/Adaptive_distance_metric_notes.tex
add

>>>>

\section{Plot of number of outliers as function $\epsilon$}

\todo[inline]{this should be done before next meeting on 2016-10-27}

\begin{itemize}
\item 
  make a plots a number of outliers as function of epsilon
+ show also the datasets which you have used and so on
\item 
  try different datasets, also generate the two gaussian mixtures
\item   find out how to export figure to EPS from AIMMS
\item  change a copy of {\bf output scatter plot} to use the learnt distance measure
\end{itemize}
